PhD Studentship: Using artificial intelligence to improve decision-making

### 2018-07-24 notebook/opportunities/IAPETUS_AI_PhD.Rmd
add IAPETUS stuff

---
title: "PhD Studentship: Using artificial intelligence to improve decision-making in conservation conflicts"
author: ""
date: ""
output: html_document
---

@@

[4] Duthie, AB, et al. (2018). GMSE: an R package for generalised management strategy evaluation. Methods in Ecology and Evolution. In review. (pre-print here)

>>>>

---
title: 'PhD Studentship: Using artificial intelligence to improve decision-making
  in conservation conflicts'
author: ''
date: ''
output:
  html_document: default
  word_document: default
---

@@

[4] Duthie, AB, et al. (2018). GMSE: an R package for generalised management strategy evaluation. Methods in Ecology and Evolution. In review. (pre-print [here](https://www.biorxiv.org/content/early/2018/05/16/221432))
